Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-03 trunk/constantRate/ConstCompFuzzExt.tex
proof of security of construction

\begin{definition}
Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.  Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \epsilon_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \epsilon_{code}$.
\end{definition}

@@

%\bnote{I don't think we need this!}
%\begin{definition}
%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
%\end{definition}
%All binary linear codes~(without constant bits) are output equiprobable and .  This is true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.
%
%\begin{lemma}
%\label{lem:linear codes independent}
%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
%\end{lemma}
%Proof in \apref{sec:proof of linear indep}.
%
%

@@

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
$(\neigh_t, \epsilon_{code})$-error-correcting code.
We describe $\gen, \rep$ as follows:

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.  We discuss  block unguessable distributions in \apref{sec:characterize}.
To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable \onote{fix}.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ \onote{is small}.
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ \onote{fix: making polynomial number of oracle queries to $\mathcal{O}_X$}cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$. \onote{sounds like VGB is enough}
This is done in \lemref{lem:sim cannot distinguish}.
% the following steps:
%\begin{itemize}
%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).
%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
%\end{itemize}
\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
\end{itemize}

\noindent Together these arguments allow us to conclude: \onote{Shouldn't this theorem have a proof? All of these parameter do not seem to follow trivially from the bullet points before.}
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator \bnote{grey box?} with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

\begin{lemma}
\label{lem:correct of cons}
Let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\epsilon_{code}\right).
\]
That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
\end{lemma}

@@

Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
\begin{theorem}
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \epsilon_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\epsilon_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
\end{theorem}
\begin{proof}
Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.  Correctness follows from \lemref{lem:correct of cons}.
\end{proof}

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  We use an algorithm that draws random samples from block sources.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.   Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.  Define $\gen, \rep$ as:

@@

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  Let $t'$ be the capacity of $C$.  To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.  Let $t$ be the number of supported errors between $w$ and $w'$.  Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
\end{align*}
Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=\alpha - \log |A'|\\
&=\alpha - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}
In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} captures this type of distribution.
We now consider more complicated distributions where blocks are not independent.

@@

Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.  We can prove a similar claim in the case where $f$ is not injectiveall blocks do not a source~(determined by $f$).

\begin{claim}
\label{cl:all blocks entropy}
Let $W = W_1,..., W_\ell$ be a source.  Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, $\alpha ' = \omega(\log n)$, $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
\end{claim}
\begin{proof}
Consider a particular block $W_i$, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
\begin{align*}
\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}]\\
&\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
\end{align*}
It suffices to show that $\Pr[\text{some non zero response}] = \ngl(n)$ and that $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = \ngl(n)$.  We show each of these is turn.

@@

\section{Proof of \thref{thm:security of cons}}
\noindent
We now prove $S$ cannot distinguish between $C$ and $C'$.
Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

@@

>>>>

\begin{definition}
Let $\neigh_t(c)$ be as in \defref{def:hamming z channel}.  Then a set $C$~(over $\zo^\ell$) is a $(\neigh_t, \delta_{code})$-code if there exists an efficient procedure $\rec$ such that for all $c\in C, \forall c'\in \neigh(c), \Pr[\rec(c') \neq c] \leq \delta_{code}$.
\end{definition}

@@

%\bnote{I don't think we need this!}
%\begin{definition}
%A binary $(\neigh_t, \delta_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
%\end{definition}
%All binary linear codes~(without constant bits) are output equiprobable and .  This is true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.
%
%\begin{lemma}
%\label{lem:linear codes independent}
%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
%\end{lemma}
%Proof in \apref{sec:proof of linear indep}.
%
%

@@

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
$(\neigh_t, \delta_{code})$-error-correcting code.
We describe $\gen, \rep$ as follows:

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries  
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.
We discuss  block unguessable distributions in \apref{sec:characterize}.  \consref{cons:first construction} is secure for block unguessable distributions:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual gray box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

We give a brief outline of the proof here, the full proof is in \apref{app:security of main cons}.
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}}(C)$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}}(C) \approx S^{\mathcal{O}}(C')$. 
\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$.
\end{itemize}

@@

\begin{lemma}
\label{lem:correct of cons}
Let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then when $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{2^n}+\delta_{code}\right).
\]
That is, \consref{cons:first construction} is correct with error at most $\ell/2^n$.
\end{lemma}

@@

Together, with the arguments in \secref{sec:sec of construction} we have the construction is secure and correct for block unguessable distributions:
\begin{theorem}
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable distributions over $\zo^{n\times \ell}$ for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\zo^{n\times \ell}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(s_{sec}, \epsilon_{sec})$ with error $\delta_{code} + \ell/2^n$ and resulting entropy $\tilde{m} =\log |C| - \beta$.
\end{theorem}
\begin{proof}
Security is a result of \thref{thm:security of cons} because $2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}$ is negligible when $\epsilon_{obf} = \ngl(n), \ell = \poly(n)$ and $\alpha =\omega(\log n)$.  Correctness follows from \lemref{lem:correct of cons}.
\end{proof}

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  We use an algorithm that draws random samples from block sources.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.   Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable obfuscator\bnote{right def?} for the family of point functions over $\zo^\eta\times \mathcal{Z}$.  Define $\gen, \rep$ as:

@@

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  Let $t'$ be the capacity of $C$.  To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.  Let $t$ be the number of supported errors between $w$ and $w'$.  \bnote{should really use something other than $c$ here}
Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
\end{align*}
Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of blocks such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we ignore all other blocks as they are independent).
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary~(we assume the best coins are in nonuniform advice).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=\alpha - \log |A'|\\
&=\alpha - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} captures this type of distribution.

However, \defref{def:block guessable} captures considerably more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.  We can prove a slightly weaker claim when the correlation between $W_i$ is arbitrary:

\begin{claim}
\label{cl:all blocks entropy}
Let $W = W_1,..., W_\ell$ be a source.  Let $\alpha =\omega(\log n)$ and suppose that for all $i$ $\Hoo(W_i)\geq \alpha$, then for $q = \poly(n)$, there exists a $\alpha ' = \omega(\log n)$ such that $W$ is a $(q, \alpha', \ell)$-block unguessable distribution.
\end{claim}
\begin{proof}
Consider a particular block $W_i$, it suffices to show that $\Hav(W_i | Q_1,A_1,..., Q_q, A_q) \geq \omega(\log n)$.  By the definition of conditional min-entropy:
\begin{align*}
\Hav(W_i | Q_1, A_1,..., Q_q, A_q) &= -\log (\Pr[\text{some non zero response}] \max_{w\in W_i} \Pr[W_i | \text{non zero response}) \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i| \text{all zero responses}]\\
&\geq-\log (\Pr[\text{some non zero response}]\times 1 \\&+ \Pr[\text{all zero responses}]\max_{w\in W_i} \Pr[W_i = w_i | \text{all zero responses}]).
\end{align*}
It suffices to show that $\Pr[\text{some non zero response}] = \ngl(n)$ and that $\max_{w\in W_i} \Pr[W_i | \text{all zero responses}] = \ngl(n)$.  We show each of these is turn.

@@

\section{Proof of \thref{thm:security of cons}}
\label{app:security of main cons}
\begin{proof}

Let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to how that $H^{\hill}_{\epsilon', s_{obf}}(C|P)\geq |C|- \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.  Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]

Let $D$ be some distinguisher of size at most $s_{obf}$.  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $s_{obf}$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)] |\leq \epsilon_{obf}.
\end{align}

We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

@@

\noindent Now by the security of obfuscation we have that 
\begin{align}
\label{eq:dist after}
|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\leq \epsilon_{obf}.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
\begin{align*}
\delta^{D}(( P, C), (P, C'))&\leq |\expe \expe [D(P_1,..., P_\ell, C)] - \expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C)]| \\
&+|\expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C)] - \expe[S^{\mathcal{O}_X(\cdot, \cdot)}(C')] |\\
&+|\expe [S^{\mathcal{O}_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
&\leq \epsilon_{obf} + (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{obf}.
\end{align*}
This completes the proof of \thref{thm:security of cons}.
\end{proof}
